---
title: "RPresentation assignment: Data description"
author: "Ignacio Garcia Sanchez-Migallon"
font-family: 'Courier New'
date: "26/2/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default---
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
rm(list=ls())
data(esoph)
library(ggplot2)
library(tidyverse)
library(plotly)
```

## Introducion : Esophageal cancer data 

The selected data comes from a case-control study of esophageal cancer in Ille-et-Vilaine, France.
It is composed by the following attributes:

- Age group
- Alcohol consumption group
- Tobacco consumption group
- Number of cancer cases registered for this group
- Total of subjects in this group



## Age group

Age group is composed by the following groups:

- 35-34 years old
- 35-44 years old
- 45-54 years old
- 55-64 years old
- 65-74 years old
- 75+ years old

## Age group

```{r group}


plot = esoph %>% ggplot(mapping =  aes(x = esoph$agegp, y = esoph$ncases)) + 
geom_bar(stat = 'identity', position = position_dodge()) + 
labs(title = 'Esophageal cancer patients by age group', x = 'Age group', y = 'Number of cases') +
theme_classic()

ggplotly(plot)

```

## Alcohol consumption

Alcohol consumption is organized in groups based on daily alcohol intake measured in grams:

- 0-39g a day
- 40-79g a day
- 80-119g a day
- +120g a day

## Alcohol consumption

```{r alcohol}
plot = esoph %>%
ggplot(mapping =  aes(x = alcgp, y = ncases, fill = agegp)) + 
geom_bar(stat = 'identity', position = position_dodge()) + 
labs(title = 'Esophageal cancer patients by alcohol consumption', x = 'Alcohol consumption', y = 'Number of cases') +
theme_classic()

ggplotly(plot)

```

## Tobacco Consumption

Tobacco consumption is organized in groups based on cigaretters smoked per day:

- 0-9 cigarettes smoked per day
- 10-19 cigarettes smoked per day
- 20-29 cigarettes smoked per day
- 30+ cigarettes smoked per day

## Tobacco Consumption

```{r tobacco}
plot = esoph %>%
ggplot(mapping =  aes(x = tobgp, y = ncases, fill = agegp)) + 
geom_bar(stat = 'identity', position = position_dodge()) + 
labs(title = 'Esophageal cancer patients by tobacco consumption', x = 'Tobacco consumption', y = 'Number of cases') +
theme_classic()

ggplotly(plot)

```


